Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-18 WRITEUP/ms.tex
done photometry section

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}

@@

\section{HST astrometry}
We obtain HST images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical (V$-$band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2") of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

@@

\subsection{Photometry}
We compiled/web-scraped the \mir to \fir photometry
from 2MASS, WISE, IRAS, IRAC catalogs .
to characterize
the dust emission in RXJ1131 from
from the 2MASS All-Sky Catalog of Point Sources  (Skrutskie et al. 2006), WISE
magnitudes from the AllWISE Source CatalogBLAH, Spitzer/MIPS
data from BLAH Catalog, IRAS photometry from the IRAS point source
and faint source cataloguesBLAH.

We extract the Herschel/SPIRE photometry using SUSSEXTractor
within HIPE (Savage \& Oliver 2007, Smith et al 2012, Pearson et al 2014)
over the data obtained from the Herschel Science Archive, which were
processed by the SPIRE HIPE pipeline version 12BLAH (Ott 2010).
The SUSSEXtractor
task estimates the flux density from an image smoothed with
a convolution kernel derived from the SPIRE beam FWHM.
The flux density measured by SUSSEXtractor
was verified using the SPIRE Timeline Fitter (Bendo et
al. 2013) which fits a two dimensional elliptical Gaussian
function at the source position in the timeline data. The
agreement between the SUSSEXtractor and Timeline Fitter
flux densities was found to be better than $\sim$BLAH per cent.

We list the photometry from optical to radio in \Tab{photometry}.
\input{table_photometry_AAScustomized}

@@

\subsection{SED modeling}
\subsection{ISM properties}
\subsection{Gas Mass}
\subsection{Source Extent}
Compared to HST:

@@

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions}
We studied a wet-wet merger between a AGN/starburst ULIRG and a optically faint companion at $z$ $\sim$ 0.65.
In this paper, we BLAH, refining the redshift to $z_{\rm CO}$=0.65370$\pm$0.0005.

>>>>

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
We use a concordance $\Lambda$CDM cosmology throughout this paper, with parameters from the WMAP9 results: $H_0$ = 70 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.27, and $\Omega_{\Lambda}$ = 0.7 \citep{Hinshaw13a}.

@@

\section{HST astrometry} %DONE
We obtain HST images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical (V$-$band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2") of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

@@

\subsection{Photometry} \label{sec:photometry} %DONE
We compile \mir to \fir broadband photometry from various
catalogs available on the NASA/IPAC Infrared Science
Archive (IRSA) in \Tab{photometry}. These data were obtained from
the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
Wide-field Infrared Survey Explorer (WISE; \citealt{Wright10a}),
{\it Infrared Astronomical Satellite} (IRAS; \citealt{Neugebauer84a}), and
the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
\spitzer. We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
Spitzer Heritage Archive. We perform aperture photometry on
the channel 1 image to extract flux density at 3.6\,$\mu$m
since it is not available from the IRSA archive.

The emission in the IRAC images is slightly extended. We thus use the
HST image ($\sim$0\fracs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy. We use the average
FWHM found by fitting a Gaussian profile to several field stars
using \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
The details of the SED modeling is presented in \Sec{SED}.

Extraction of the {\it Herschel}/SPIRE photometry was
carried out using SUSSEXTractor within Herschel Interactive
Processing Environment (HIPE; \citealt{Ott10a})
over the Level 2 maps obtained from the Herschel Science Archive.
These maps were processed by the SPIRE pipeline
version 13.0 within HIPE. The SUSSEXtractor task estimates
the flux density from an image convolved with a kernel
derived from the SPIRE beam. The flux density
measured by SUSSEXtractor is additionally confirmed
using the Timeline Fitter. This task performs photometry
by fitting a 2D elliptical Gaussian to the Level 1 data at the
source position given by the output of SUSSEXtractor.

\input{table_photometry_AAScustomized}

@@

\subsection{SED modeling}

We extrapolated a power-law to 24 \micron
to decompose the flux at 24 \micron in MIPS.

\subsection{ISM properties}
\subsection{Gas Mass}
\subsection{Source Extent}
Compared to HST:

@@

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions}
We observed the cold molecular gas properties using \bco and \cco line emission
toward the AGN host galaxy RXJ1131 at $z_{\rm CO}$\,$\sim$0.65.
Our results suggest that RXJ1131 is a wet-wet merger between a AGN/starburst
ULIRG and a optically faint companion.
